\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-10-29 AffineLieAlgebras/InformalNotes/article.tex
Equations labels fixed.

Character reduction
\begin{equation}
  \label{eq:19}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Numbers $b^{(\mu)}_{\nu}$ are called branching coefficients.

@@

Here we present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
\begin{equation}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
\end{equation}
The proof of the formula and definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.

@@

Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.

Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W/W_{\bot}$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:1}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (0,1),\; (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

In the orthogonal basis $e_1,\dots,e_4$ simple roots of $B_4$ are
\begin{equation}
  \label{eq:1}
  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4)
\end{equation}
Positive roots are
\begin{multline}
  \label{eq:2}
  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\\
    e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2)
\end{multline}
Simple roots of the embedded subalgebra $\mathfrak{a}=B_2$ are
\begin{equation}
  \label{eq:3}
  (e_3-e_4,e_4)
\end{equation}

The set $\Delta_{\bot}$ is equal to
\begin{equation}
  \label{eq:4}
  \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
\end{equation}

>>>>

Character reduction
\begin{equation}
  \label{eq:28}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Numbers $b^{(\mu)}_{\nu}$ are called branching coefficients.

@@

Here we present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
\begin{equation}
  \label{eq:1}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
\end{equation}
The proof of the formula and definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.

@@

Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$. To prove it we should show that for any two positive roots $\alpha,\; \beta\in \Delta_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$ there exists Weyl reflection $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}\in W_{\bot}$ and the corresponding positive root $\gamma\in \Delta_{\bot}$. Since root space of the subalgebra $\mathfrak{a}$ is invariant under $\omega_{\alpha}, \; \omega_{\beta}$ it is also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$. Then the positive root $\gamma in \Delta^{+}$ which corresponds to $\omega_{\gamma}$ is orthogonal to the root space of $\mathfrak{a}$ and hence $\gamma\in \Delta_{\bot}$.

Since $W_{\bot}$ is the subgroup of $W$ and the space spanned over the set $\Delta_{\bot}$ is invariant under its action there exists a  subalgebra with the root space spanned over the set $\Delta_{\bot}$ which we denote by $\mathfrak{a}_{\bot}$.

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W/W_{\bot}$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (0,1),\; (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

In the orthogonal basis $e_1,\dots,e_4$ simple roots of $B_4$ are
\begin{equation}
  \label{eq:8}
  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4)
\end{equation}
Positive roots are
\begin{multline}
  \label{eq:19}
  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\\
    e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2)
\end{multline}
Simple roots of the embedded subalgebra $\mathfrak{a}=B_2$ are
\begin{equation}
  \label{eq:26}
  (e_3-e_4,e_4)
\end{equation}

The set $\Delta_{\bot}$ is equal to
\begin{equation}
  \label{eq:27}
  \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
\end{equation}
